Regional Base-Flow Index in Arid Landscapes Using Machine Learning and Instrumented Records

### 2025-01-20 MANUSCRIPT.qmd
supp info

|   | Variable | Source | Geoprocessing |
|------------------|-------------------|------------------|------------------|
| Hydroclimate | Precipitation\* | PRISM | Basin average |
|  | Mean Temperature\* | PRISM | Basin average |
|  | Reference Evapotranspiration\* | TerraClimate | Basin average |
| Geospatial | Elevation\* | DEM | Basin average |
|  | Area | DEM | Basin average |
|  | Slope | DEM | Basin average |
|  | Aspect | DEM | Percent areal coverage |
|  | Land Cover\* | NLCD | Percent areal coverage |
|  | Hydrologic Soil Group\* | SSURGO | Percent areal coverage |
|  | Geology | USGS | Percent areal coverage |
|  | Karst | USGS | Percent areal coverage |

@@

| **Classification Group** | **n** | **n_pos** | **n_neg** | **perc_pos** | **perc_neg** |
|------------|------------|------------|------------|------------|------------|
| Precipitation - Monsoon Dominated | 87 | 8 | 21 | 0.092 | 0.241 |
| Precipitation - Snowmelt Dominated | 118 | 9 | 12 | 0.076 | 0.102 |
| Physiographic Region - Basin and Range | 156 | 14 | 26 | 0.090 | 0.167 |
| Physiographic Region - Colorado Plateau | 49 | 3 | 7 | 0.061 | 0.143 |
| Climate - Warm-Wet | 31 | 2 | 6 | 0.065 | 0.194 |
| Climate - Warm-Dry | 55 | 6 | 11 | 0.109 | 0.200 |
| Climate - Cool-Wet | 74 | 4 | 9 | 0.054 | 0.122 |
| Climate - Cool-Dry | 45 | 5 | 7 | 0.111 | 0.156 |
| Slope - High | 102 | 10 | 12 | 0.098 | 0.118 |
| Slope - Low | 103 | 7 | 21 | 0.068 | 0.204 |

>>>>

|   | Variable | Source | Geoprocessing |
|----|----|----|----|
| Hydroclimate | Precipitation\* | PRISM | Basin average |
|  | Mean Temperature\* | PRISM | Basin average |
|  | Reference Evapotranspiration\* | TerraClimate | Basin average |
| Geospatial | Elevation\* | DEM | Basin average |
|  | Area | DEM | Basin average |
|  | Slope | DEM | Basin average |
|  | Aspect | DEM | Percent areal coverage |
|  | Land Cover\* | NLCD | Percent areal coverage |
|  | Hydrologic Soil Group\* | SSURGO | Percent areal coverage |
|  | Geology | USGS | Percent areal coverage |
|  | Karst | USGS | Percent areal coverage |

@@

| **Classification Group** | **n** | **n_pos** | **n_neg** | **perc_pos** | **perc_neg** |
|----|----|----|----|----|----|
| Precipitation - Monsoon Dominated | 87 | 8 | 21 | 0.092 | 0.241 |
| Precipitation - Snowmelt Dominated | 118 | 9 | 12 | 0.076 | 0.102 |
| Physiographic Region - Basin and Range | 156 | 14 | 26 | 0.090 | 0.167 |
| Physiographic Region - Colorado Plateau | 49 | 3 | 7 | 0.061 | 0.143 |
| Climate - Warm-Wet | 31 | 2 | 6 | 0.065 | 0.194 |
| Climate - Warm-Dry | 55 | 6 | 11 | 0.109 | 0.200 |
| Climate - Cool-Wet | 74 | 4 | 9 | 0.054 | 0.122 |
| Climate - Cool-Dry | 45 | 5 | 7 | 0.111 | 0.156 |
| Slope - High | 102 | 10 | 12 | 0.098 | 0.118 |
| Slope - Low | 103 | 7 | 21 | 0.068 | 0.204 |
